Whole-chromosome pairwise alignment using a hierarchical wavefront algorithm

### 2021-05-31 manuscript/main.tex
added the discussion

@@

    \section*{Acknowledgements}

    Text Text Text Text Text Text Text Text.  \citealp{Boffelli03} might want to know about text
    text text text\vspace*{-12pt}

    \section*{Funding}

    This work has been supported by the... Text Text Text Text.\vspace*{-12pt}

>>>>

    We implemented a novel gap-affine pairwise aligner, \wfmash\, to accelerate the computation of the mutual
    alignment of collections of genomes, a step required for building pangenome models. We have demonstrated that
    it efficiently performs with contigs representing full human chromosomes of 88 phased haplotypes from the
    Human Pangenome Reference Consortium year 1 assembly. Indeed, thanks to its efficiency, wfmash is already
    successfully applied in our pangenome graphs building pipeline (\citep{pggb}). No less important, pairwise
    alignment is a central step of many bioinformatics applications, making our aligner a scalable solution to face the
    increasing yields of sequencing technologies in the coming years.

@@
